{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-02 Paper/main.tex

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, but only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).\\

			 This measurement set can be viewed as set of discretized approximations of the underlying true process which could be the absorption of the Near-infrared (NIR) spectrum which will be used for the simulation and application. NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyse the interaction of each other. {\color{green} For more details refer to the appendix SECTION ??!??!}. This continuous underlying process for which 
 $x_i(t)$ exists $\forall t \in [T_1, T_2]$ is only observed at the discrete measurement points. This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable. To conduct functional linear regression, several new concepts and methods need to be considered and explained that distinguish it multivariate linear regression.
%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
The focus of this paper is to introduce FLR in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	As above-mentioned, the realized curves can be estimated with basis functions. For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$. On the one hand, this way is not efficient since the technique with too many basis functions can even approximate a noise of the sample curves which possibly interrupts the analysis. On the other hand, the important information on the curves would be missed with a too-small number of basis functions. This discussion challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, maintain significant fluctuation. The basis expansion with truncation is by:
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error. The number $L$ is subjectively chosen but we can fix the nubmer through a more reasonable method, Cross-Validation, which minimizes Mean Squared Error (MSE).

@@

	In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions. In the following, all random functions are assumed to realize in $\mathbb{L}^2$. As in the finite dimensional setting the concept of identically distributed and independent data is important. This concept generalizes intuitively to the case of functional data using the concepts for general random variables. {\color{red} Explain this better!}\\
	An example of one such data set could be a set of $n$ independent realizations of a Wiener-process and $n$ associated scalar variables that could be subject of a regression analysis with respect to the corresponding realizations of the Wiener process. A definition and a plotted example for the Wiener process are given in \ref{Wiener}.

@@

	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $K$ for the estimation in SECTION HERE. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten fold cross-validation. While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a pre specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}). This might apply for this simulation as well, since certain eigenfunctions could be resulting from certain chemical combinations and overtones in the absorption bands of the spectra, that could have high predictive power, but explain only little variability of the spectra (SEE APPENDIX

	 This setup is opposing to the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high. This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation. To provide intuition in this approach, let 
	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} (Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt)^2 + \lambda * \int (D^m\beta(t))^2 dt
	 \end{equation}
	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$. A typical choice is the second derivative as highly variable functions are expected to yield large second derivatives and therefore a larger penalty. The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}

>>>>

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, but only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).

	 In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions which could be the absorption of the Near-infrared (NIR) spectrum which will be used for the simulation and application. NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyse the interaction of each other. {\color{green} For more details refer to the appendix SECTION ??!??!}.  This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable. To conduct functional linear regression, several new concepts and methods need to be considered and explained that distinguish it multivariate linear regression.
%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
The focus of this paper is to introduce FLR in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	As above-mentioned, the realized curves can be estimated with basis functions. For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$ to fit an completely unbiased estimate. This is not efficient since the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. On the other hand, the important information on the curves could be missed with a too-small number of basis functions. This discussion is subject to the Bias-Variance Tradeoff and challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, do not introduce to much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is defined by
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error. The number $L$ can be chosen subjectively, but also trough the application of a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or another criteria. The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is subject of the simulation study.

@@

	This measurement set can be viewed as set of discretized approximations of the underlying functional process:
 $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at the discrete measurement points. 
As in the finite dimensional setting, the concept of identically distributed and independent data is important. This concept generalizes intuitively to the case of functional data using the concepts for general random variables which is needed to conduct inference. {\color{red} Explain this better!}\\  The introduced concept of basis expansion of functions allow to express each observation $x_1$ as a realization of $X_1$, a random function of $\mathbb{L}^2[0,1]$.

	%In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions. In the following, all random functions are assumed to realize in $\mathbb{L}^2$.

	An example of such a dataset could be the dataset of 60 NIR-spectra of gasoline samples. Together with a set of responses, this then can be used to perform FLR, as will be subject of the simulation and application.

	% COMMENT: Maybe mention both NIR and WienerProcess? 
	%An example of one such data set could be a set of $n$ independent realizations of a Wiener-process and $n$ associated scalar variables that could be subject of a regression analysis with respect to the corresponding realizations of the Wiener process. A definition and a plotted example for the Wiener process are given in \ref{Wiener}.

@@

	 To exploit the regularity of the curves of the spectra, we introduced different basis functions in {\color{green} Link} and demonstrated the importance of the truncation parameter $K$ for the estimation in {\color{green} Link}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on selecting the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten fold cross-validation using the prediction mean-squared error. While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a pre specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}). This might apply for this simulation as well, since certain eigenfunctions could be resulting from certain chemical combinations and overtones in the absorption bands of the spectra, that could have high predictive power, but explain only little variability of the spectra {\color{green} Link to NIR}.

	 This setup is opposing to the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high. This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation. To provide intuition in this approach, let 
	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} (Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt)^2 + \lambda * \int (D^m\beta(t))^2 dt
	 \end{equation}
	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$. A typical choice is the second derivative as highly variable functions are expected to yield large second derivatives and therefore a larger penalty. The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}.
